Extrinsic Type Inference (DRAFT 2025-06-09)

### 2025-07-13 extrinsic_type_inference_paper/paper.tex
update construction of LFP for streams

>>>>

\TODO{compare inductive subtyping to tree interpolation}

\TODO{is this something we should/can prove?}

\TODO{note how CHC uses predefined constraints, while this system learns constraints from applications}

\TODO{other systems (using CHC) can construct recursive horn clauses from programs, but not local constraints, right?}

\TODO{that is the language of recursive types is used as both the constraint language and the target language}
